`infercnv` results exploration for `r params$sample_id`

### 2024-10-28 analyses/cell-type-wilms-tumor-06/notebook_template/06_cnv_infercnv_exploration.Rmd
few changes to PR828

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat_i6, features=c(glue::glue("proportion_cnv_chr", i)), group.by = "fetal_kidney_predicted.compartment"))
}
```

>>>>

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat_i6, feature=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment"))
}
```
